Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-29 ms.qmd
Add figure for life stage

###########################################################
## Model 1.4 - whether chance between q10 depends on life stage and habita
###########################################################
if(rerun){
  # More realistic model with 
  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

@@

### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*

@@

model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat + life.hist + type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

>>>>

###########################################################
## Model 1.4 - whether chance between q10 depends on life stage and habita
###########################################################
rerun = FALSE
if(rerun){
  # More realistic model with 
  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

@@

```{r}
#| label: fig-fig3
#| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.

p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))

p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())

p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())

fig3 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(fig3, filename = "./output/figures/fig3_lh.pdf", width = 8, height = 4.5)

fig3 <- magick::image_read("./output/figures/fig3_lh.pdf")
fig3

```
### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*

@@

if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)

  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)

  saveRDS(model_full_lnrr_pb, file = "./output/models/lnRRQ10_pubbias")
  saveRDS(model_full_lncvr_pb, file = "./output/models/lnCVRQ10_pubbias")
  saveRDS(model_full_lnvr_pb, file = "./output/models/lnVRQ10_pubbias")
} else {
   model_full_lnrr_pb <- readRDS(file = "./output/models/lnRRQ10_pubbias")
  model_full_lncvr_pb <- readRDS(file = "./output/models/lnCVRQ10_pubbias")
  model_full_lnvr_pb <- readRDS(file = "./output/models/lnVRQ10_pubbias")
}

summary(model_full_lnrr_pb)
```
